TBD

### 2016-08-31 paper/paper.tex
+ more related work

\section{Experiments}
\section{Related Works}
\section{Conclusions}

>>>>

\section{Experiments}
\section{Related Works}

\paragraph{Robustness analyses of closed-loop systems} The analysis in 
\cite{DBLP:conf/hybrid/WangGRJF16}
relies on an invariant computation
on the discrete system dynamics.

\paragraph{Stability analyses of closed loop systems} 
In \cite{DBLP:conf/hybrid/RouxJG15}, the authors
perform the analysis in the state space
domain using Lyapunov-based quadratic invariants.
In \cite{DBLP:journals/corr/PakmehrWJVF13}, Pakmehr et al. 
design a control software verification framework for gas turbine engines.

\paragraph{Uses of CEGIS for control sysnthesis} 
In \cite{DBLP:conf/cdc/RavanbakhshS15}, Ravanbakhsh and Sankaranarayanan use
CEGIS for the synthesis of switching
controllers for stabilizing continuous-time plants.

\section{Conclusions}
